Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-26 pirouette_article.tex
Ruthlessly moved 'candidate models' to supplementary materials, 3360 words left

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	This only increases the confusion; maybe replace by baseline model everywhere
}
\richel{
	I feel the new wording below is good enough. Replacing 'generative'
	by 'baseline' add to confustion when the generative model is the
	generative model. Giovanni, what do you think?
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline or comparison model.
}

@@

\subsection{Twinning}\label{subsec:twinning}

Similar to lab experiments, \verb;pirouette; allows to perform
a control measurement, by use of a process we call twinning. 
In this context, this control results in an error distribution
that is the baseline error of the pipeline. The difference
between the 'true' and 'twin' error distributions is caused only
by the mismatch between the (known-to-be-true or assumed) 
generative tree model and the 
tree prior used in the actual inference.

\new{
	See the supplementary materials section \ref{subsec:twinning_mathematics}
	for more details.
}

\subsection{Candidate models}\label{subsec:candidates}

The user has to specify exactly one standard inference model,
but may be unsure which one to pick. To account for this, the user can
specify a set of candidate inference models. Each of these candidate inference models is run in an initial, relatively short, analysis; the candidate model with the highest 
evidence (i.e., marginal likelihood) will then be
used in another, longer, inference run, resulting in another error distribution.
The evidence for an inference model is estimated by nested 
sampling [\cite{russel2019model}], using the \verb;NS; BEAST2 package.

If twinning is used, a candidate model that has the highest evidence for
the twin alignment is also used to create another error
distribution.

>>>>

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	This only increases the confusion; maybe replace by baseline model everywhere
}
\richel{
	I feel the new wording below is good enough. Replacing 'generative'
	by 'baseline' add to confusion when the generative model is the
	generative model. Giovanni, what do you think?
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline or comparison model.
}

@@

\subsection{Controls}\label{subsec:controls}

Similar to lab experiments, \verb;pirouette; allows to perform
two types of control measurements. The first type of control
is called 'twinning', which results in an error distribution
that is the baseline error of the inference pipeline (see
supplementary materials, section \ref{subsec:twinning} for more details).
The second type of control is the use of candidate models,
which results in an error distribution
for a generative model that is determined to be the best fit to
the tree (see supplementary materials, 
section \ref{subsec:candidates} for more details).

### 2020-06-26 pirouette_supplement.tex
Ruthlessly moved 'candidate models' to supplementary materials, 3360 words left

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The mathematics of the twinning process}
\label{subsec:twinning_mathematics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The twinning process}
\label{subsec:twinning}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Similar to lab experiments, \verb;pirouette; allows to perform
a control measurement, by use of a process we call twinning. 
In this context, this control results in an error distribution
that is the baseline error of the pipeline. The difference
between the 'true' and 'twin' error distributions is caused only
by the mismatch between the (known-to-be-true or assumed) 
generative tree model and the 
tree prior used in the actual inference.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Candidate models}
\label{subsec:candidates}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The user has to specify exactly one standard inference model,
but may be unsure which one to pick. To account for this, the user can
specify a set of candidate inference models. Each of these candidate inference models is run in an initial, relatively short, analysis; the candidate model with the highest 
evidence (i.e., marginal likelihood) will then be
used in another, longer, inference run, resulting in another error distribution.
The evidence for an inference model is estimated by nested 
sampling [\cite{russel2019model}], using the \verb;NS; BEAST2 package.

If twinning is used, a candidate model that has the highest evidence for
the twin alignment is also used to create another error
distribution.
